P.berghei pir analysis

### 2021-08-31 Manuscript_pirAnalysis_Github/Pberghei/Manuscript_Github_Pberghei_pir.Rmd
Do name changes and cluster analysis on big TPM df

@@

```{r remove_E06-6h}
#Remove the Caldelari (E06) 6h samples, as they did in their paper.

expt_tpms$E06$tpm <- select_at(expt_tpms$E06$tpm,
                                          vars(-matches('Liv-6h')))
```

@@

```{r hclusts, message = FALSE}

lapply(expt_tpms, function(tpm){
  if(ncol(tpm$tpm) > 3){
    dists = dist(t(tpm$tpm[,-1]))
    par(cex=0.7)
    plot(hclust(dists),
         main = tpm$experiment)
  }
})
```

@@

@@

@@

big_tpm <- bind_cols(
  lapply(
    expt_tpms,
    function(x){
      tpm_df <- x$tpm
      colnames(tpm_df)[-1] <- paste0(x$experiment,
                                     '_',
                                     colnames(tpm_df)[-1])
      tpm_df
    }
  )
) %>% 
  dplyr::rename(Geneid = Geneid...1) %>% 
  select_at(vars(-matches('Geneid\\.\\.\\.\\d+$'))) %>% 
  data.frame

rownames(big_tpm) <- big_tpm$Geneid

big_tpm <- big_tpm[,-1,drop=FALSE]

>>>>

```{r remove_E06-6h}
#Remove the Caldelari (E06) 6h samples, as they did in their paper.
berghei_tpm[,str_subset(colnames(berghei_tpm), 'E06_Liv.6h')] <- NULL
```

```{r hclusts, message = FALSE}
experiment_id <- unique(na.omit(str_extract(colnames(berghei_tpm), pattern = 'E[[:digit:]]{2}')))

lapply(experiment_id, 
       function(experiment_name){
         tpm_data <- select(berghei_tpm, matches(experiment_name))
         if(ncol(tpm_data) > 3){
           dists = dist(t(tpm_data))
           par(cex=0.7)
           plot(hclust(dists),
                main = experiment_name)
         }
       })

```{r combine_similar_samples_byNames}
col_stage <- colnames(berghei_tpm)

#Combine all Liver samples 4h or before into LiverPre4h
col_stage <- str_replace_all(col_stage,
                             pattern = 'Liv\\.(2|4)h_[[:digit:]]+',
                             replacement = 'Liv.pre4h')
#Combine all Liver samples 48h or onwards into LiverPost48h
col_stage <- str_replace_all(col_stage,
                             pattern = 'Liv\\.(4[8-9]|[5-9][0-9])h_[[:digit:]]+',
                             replacement = 'Liv.post48h')
#Combine all blood meal samples 3h or before into BldMlPre3h
col_stage <- str_replace_all(col_stage,
                             pattern = '(1h|3h)_[[:digit:]]+', 
                             replacement = 'Pre3h')
#Uniquify the name names
col_stage[grep(col_stage, 
               perl = TRUE,
               invert = TRUE,
               pattern = '_[[:digit:]]{1,}$')] <- uniquify(col_stage[grep(col_stage, 
                                                                          perl = TRUE,
                                                                          invert = TRUE,
                                                                          pattern = '_[[:digit:]]{1,}$')]) 
```

@@

@@

@@

```{r big_tpm}

@@

write.csv()
```

@@
